Minimizing post-shock forecasting error using disparate information

### 2020-08-09 manuscript/alphahist.tex
addition of simulation results

% Created by tikzDevice version 0.12.3.1 on 2020-08-05 11:58:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 66.75, 26.40) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (133.70, 26.40) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (200.65, 26.40) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (267.60, 26.40) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (334.56, 26.40) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (401.51, 26.40) {7};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (468.46, 26.40) {8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (535.41, 26.40) {9};

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.25, 55.15) -- (167.18, 85.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.18, 85.07) -- (188.30,106.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,220.75) -- (213.70,233.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,118.55) -- (234.13,152.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.13,152.02) -- (239.34,157.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.46, 55.15) -- (267.60, 83.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.60, 83.29) -- (301.08,116.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (301.08,116.77) -- (334.56,150.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56,150.24) -- (368.03,183.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.66, 55.15) -- (368.03, 81.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.03, 81.52) -- (401.51,114.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.87, 55.15) -- (443.87, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.46, 79.74) -- (469.39, 80.67);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.22, 55.15) --
	(133.70, 55.15) --
	(133.70,106.19) --
	(100.22,106.19) --
	(100.22, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.70, 55.15) --
	(167.18, 55.15) --
	(167.18,106.19) --
	(133.70,106.19) --
	(133.70, 55.15);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.27, 48.00) -- (282.27,240.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.44,226.14) -- (285.62,226.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.00,228.67) --
	(285.62,226.14) --
	(290.00,223.61);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (368.03,223.64) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$5.22};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-08 20:35:31
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 66.75, 26.40) {7};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (133.70, 26.40) {8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (200.65, 26.40) {9};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (267.60, 26.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (334.56, 26.40) {11};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (401.51, 26.40) {12};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (468.46, 26.40) {13};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (535.41, 26.40) {14};

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.11, 55.15) -- (133.70, 79.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.70, 79.74) -- (167.18,113.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,146.69) -- (234.13,180.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.31, 55.15) -- (234.13, 77.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.13, 77.96) -- (267.60,111.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.60,111.44) -- (287.88,131.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (301.08,144.91) -- (334.56,178.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.52, 55.15) -- (334.56, 76.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56,178.39) -- (364.44,208.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56, 76.19) -- (368.03,109.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.03,109.66) -- (401.51,143.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.72, 55.15) -- (434.98, 74.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.93, 55.15) -- (535.41, 72.63);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.22, 55.15) --
	(133.70, 55.15) --
	(133.70, 80.67) --
	(100.22, 80.67) --
	(100.22, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.70, 55.15) --
	(167.18, 55.15) --
	(167.18,131.71) --
	(133.70,131.71) --
	(133.70, 55.15);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.53, 48.00) -- (282.53,240.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.70,226.14) -- (285.88,226.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.26,228.67) --
	(285.88,226.14) --
	(290.26,223.61);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (374.73,223.64) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$10.22};
\end{scope}
\end{tikzpicture}
